---
title: "Reproducible Pitch and Shiny Application"
author: "Andreas Chaniotis"
date: "12/01/2022"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Description of the Project

This assesment is part of the course Developing Data Products as part of the Coursera Data Science Specialization course.

Instructions:

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github


## How to use the application
Using the data from mtcars, we are ploting the histogram of couple of variables.
The user can choose the variable and change the number of bins to us.

the application is runing on (https://achaniotis.shinyapps.io/shiny_application/)

ui.R, and Server.R Code in my github repository
(https://github.com/andreaschaniotis/Shiny-Application-and-Reproducible-Pitch)


## mtcars Dataset

The data used in the app comes from the mtcars dataset. 

```{r }

mtcars2 <- within(mtcars, {
   vs <- factor(vs, labels = c("V", "S"))
   am <- factor(am, labels = c("Automatic", "Manual"))
   cyl  <- ordered(cyl)
   gear <- ordered(gear)
   carb <- ordered(carb)
})
summary(mtcars2)


```

## Example plot of the applications
In the below plot is an example of the plot when choosing "mpg" and 30 bins:
```{r }
 hist(mtcars2$mpg, breaks = 30, col = 'darkgray', border = 'white', xlab="mpg", main="Historgram of mpg")
```

